Appendix0\_10

### 2018-08-17 paper/Appendices/AppendixC.tex
appendix done

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics{Figures/CW2level1.png}
	\decoRule
	\caption[2 Classes solution in Day level]{2 Classes solution in Day level.}
	\label{fig:diary1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB2.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 2).]{Multilevel Latent Class Solution, 2 classes in day level, 2 classes in individual level.}
	\label{fig:diary1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB3.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 3).]{Multilevel Latent Class Solution, 2 classes in day level, 3 classes in individual level.}
	\label{fig:diary1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB4.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 4).]{Multilevel Latent Class Solution, 2 classes in day level, 4 classes in individual level.}
	\label{fig:diary1}
\end{figure}

@@

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW3CB4.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (3 $\times$ 4).]{Multilevel Latent Class Solution, 3 classes in day level, 4 classes in individual level.}
	\label{fig:diary1}
\end{figure}

@@

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=15cm]{Figures/CW4level1.png}
	\decoRule
	\caption[2 Classes Solution in Day level]{4 Classes Solution in Day level.}
	\label{fig:diary1}
\end{figure}

>>>>

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics{Figures/CW2level1.png}
	\decoRule
	\caption[2 Classes solution in Day level]{2 Classes solution in Day level.}
	\label{fig:CW2level1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB2.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 2).]{Multilevel Latent Class Solution, 2 classes in day level, 2 classes in individual level.}
	\label{fig:CW2CB2}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB3.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 3).]{Multilevel Latent Class Solution, 2 classes in day level, 3 classes in individual level.}
	\label{fig:CW2CB3}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW2CB4.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (2 $\times$ 4).]{Multilevel Latent Class Solution, 2 classes in day level, 4 classes in individual level.}
	\label{fig:CW2CB4}
\end{figure}

@@

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW3CB4.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (3 $\times$ 4).]{Multilevel Latent Class Solution, 3 classes in day level, 4 classes in individual level.}
	\label{fig:CW3CB4}
\end{figure}

@@

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=15cm]{Figures/CW4level1.png}
	\decoRule
	\caption[2 Classes Solution in Day level]{4 Classes Solution in Day level.}
	\label{fig:CW4level1}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW4CB2.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (4 $\times$ 2).]{Multilevel Latent Class Solution, 4 classes in day level, 2 classes in individual level.}
	\label{fig:CW4CB2}
\end{figure}

\begin{figure}[H]
	%\vspace*{13cm}
	\centering
	\includegraphics[width=13cm]{Figures/CW4CB3.png}
	\decoRule
	\caption[Multilevel Latent Class Solution (4 $\times$ 3).]{Multilevel Latent Class Solution, 4 classes in day level, 3 classes in individual level.}
	\label{fig:CW4CB3}
\end{figure}
